%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Yisheng Gong} \\ \vspace{1pt}
    \small +1 314-904-6457(US) $|$ \href{mailto:x@x.com}{{yishenggong9437@gmail.com}} $|$ \href{https://www.linkedin.com/in/yisheng-gong1997}{{linkedin}} $|$
    \href{https://www.github.com/gongyisheng}{{github}} $|$ \href{https://yishenggong.com}{{website}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Washington University in St.Louis}{St.Louis, MO}
      {Master of Science in Business Analytics}{Jan 2021 -- May 2022}
    \resumeSubheading
      {Fudan University}{Shanghai, China}
      {Bachelor of Science in Chemistry }{Sept 2015 -- June 2019}
  \resumeSubHeadingListEnd

  %
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Golang, Java, SQL, C/C++, Javascript} \\
     \textbf{Software}{: Databricks, Spark, Git, Nginx, Kubernetes, Docker, Grafana, Prometheus} \\
     \textbf{Database}{: MySql, PostgreSQL, Redis, MongoDB, ElasticSearch} \\
     \textbf{Linux tools}{: Ubuntu 22, tcpdump/wireshark, netstat, perf, trace}\\
     \textbf{Cloud}{: AWS EC2/S3/RDS/Elasticcache/Lambda} \\
     \textbf{Interests}{: performance improvement, network, database}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer}{June 2022 -- }
      {Yipitdata, Edison Platform Team}{Mountain View, CA, US}
      \resumeItemListStart
      \resumeItem{Maintained a mulit-million ETL data pipeline. Migrated pipeline from AWS EMR to Databricks. Optimized the weekly refresh pipeline's performance and achieve 60\% reduce in run time and 40\% cost cut. Set up automatic data quality check on pipeline delivery to find out issues in time.}
        \resumeItem{Maintained Edison Mail's email extraction service. Improved service's performance by 55\% and achieved 70\% cost cut through profiling, caching time-consuming function's result and reducing duplicated function calls. Helped the team make faster respond to client's requests.}
        \resumeItem{Designed and implemented Redis client side cache with python asyncio and redis client tracking. Reduced I/O requests by 90\% in Edison mail's extraction service and and achieved real-time updates}
        \resumeItem{Designed and implemented a generalized streaming sync system using MySQL binlog and redis stream. Refactor the system to be event-driven. Achieved real-time data sync for online search service and legal demand.}
      \resumeItemListEnd
    \resumeSubheading
      {Software Engineer, Part Time}{Jan 2022 -- May 2022}
      {Massachusetts Institute of Technology, ChemE, CRIPT Team}{Remote, US}
      \resumeItemListStart
        \resumeItem{Designed and Developed an open-source, semi-automated data ingestion tool based on excel spreadsheet and CRIPT sdk for chemists to upload experiment data to CRIPT database using python. Designed the tool with a compiler-like structure. Assisted early users to upload about 100 thousand data points to database.}
        \resumeItem{Created unit tests for the data ingestion tool, fixed 20+ bugs based on self testing and user feedback.}
      \resumeItemListEnd
    \resumeSubheading
      {Data Engineer Intern}{Jan 2021 -- May 2021}
      {Bytedance(TikTok), Group of Douyin E-commerce, Commercialization Division}{Beijing, China}
      \resumeItemListStart
        \resumeItem{Developed ETL pipeline with 30+ dependencies to process collected raw data and store in Hbase using HiveSQL. Developed 4 DM tables with different aggregation degrees to satisfy needs. Separated DW data from business logic. Supported the data needs of 200+ colleagues from data science team and operation team.}
        \resumeItem{Collaborated with team members to implement a regression model to evaluate GMV increment of sales promotion tools using SQL and python. Visualized results with matplotlib. Deployed the model to perform daily update.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}

